\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}

\title{Peer Reviews}

\author{Jesse Wilson}

\date{\today}

\begin{document}
\maketitle

\section{Yuan Zhang}

Yuan was overall a very good group mate. I was able to work well with him throughout the projects. He was always helpful and a hard worker and fought stubbornly to see the project through to completion, even after running into numerous bugs. If it wasn't for his efforts, we may not have not been able to complete a couple of the projects. He always managed to find the little bugs that Daniel and I overlooked. Where we would think everything was correct, he would spot the little typo that was preventing the code from compiling properly. 

That being said, Yuan wasn't always the quickest to respond to emails and rarely would take the initiative to organize group meetings. Not entirely a fault of his own, but he was often so busy with his other classes that I wouldn't hear back from him on meeting times for a quite a few days. This is only a minor grip and isn't worth fussing about though. I appreciated his drive to solve the problems presented in the class and it always encouraged me to continue to work late into the evening on a project when I was tired and just wanted to give up and go home.

The majority of Yuan's contributions came in the later parts of the projects. He often struggled with finding a place to start on the projects, but once we got going and had the framework for the project, he would take off and start setting it up in his VM. 

Overall, Yuan was a good group mate and I would have no problems working with him again on any future project.


\section{Daniel Tasato}

I must admit, I was a little worried about Daniel in the begining of the class. We were all pretty lost with the first couple projects, but he seemed especially lost. He didn't have the strongest grasp on Linux or the terminal and it all seemed pretty foreign to him. However, as we started getting into it, he started helping more and putting in more effort. He was especially helpful in the concurrent assignments and nearly did the second one by himself before we realized what he was doing. He never seemed to understand the material as well as Yuan or I did, but he didn't stop trying to and he continued to put effort in to the last project. 

With only a couple exceptions, Daniel was quite good at responding to emails and showing up to group meetings when we planned them. Whenever he wasn't going to be on time, he would let me know via email and make sure it was ok if he was a little late. It was never a problem. 

Daniel was also a good group mate and where he didn't have the understanding of the material that Yuan did, he always showed up to meetings and he always tried his best to help; contributing all the while.  I would not have a problem working with him again.


\end{document}
